### 2021-11-06 paper/manuscript.Rmd
Update Results Manuscript

The second largest marginal effect was that of the estimated model. All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms performed worst for the linear model. There again was little difference in performance between the Pema algorithms and RMA, altough MetaForest performed worst. Image 2 shows the relationship.

@@

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, altough there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 11 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

@@

Finally, there seemed to be an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 20 shows the interaction. This relationship was reversed for $TP$ and was found for all algorithms, i.e. $TP$ decreased as the number of moderators increased.

>>>>

The second largest marginal effect was that of the estimated model. All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms performed worst for the linear model. There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst. Image 2 shows the relationship.

@@

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 11 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

@@

Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 20 shows the interaction. This relationship was reversed for $TP$ and was found for all algorithms, i.e. $TP$ decreased as the number of moderators increased.
